The vertical Fermi and eROSITA bubbles inclined jets: A proof-of-concept study

### 2021-12-19 paper.tex
update

  A crucial ingredient in the simulations is the clumpy ISM disk,\
  in which the temperature ranging from

>>>>

  A crucial ingredient in our work is the clumpy ISM disk initialized by\
  the publicly available pyFC code
  \footnote{\url{https://pypi.python.org/pypi/pyFC}}.
  The spatial density distribution $\rho(\bold{x})$ of clumpy ISM obeys\
  the log-normal probability distribution in real space,\
  and the Kolmogorov power spectrum in the Fourier space.
  \begin{equation}
    D(k)=\int k^{2} \hat{\rho}(k)\hat{\rho}^{*}(k)dk \propto k^{-5/3},
  \end{equation}
  where $\hat{\rho}(k)$ is the Fourier transform of $\rho(\bold{r})$.

  \citet{LA2002} and \citet{Wagner2012} have outlined a detailed procedure\
   for constructing clumpy structure, and we do not repeat here.
